\mytitle

### 2017-10-27 paper.tex
nits

The second problem is that most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services, 
developers often have to rewrite their code to orchestrate server programs into 
the narrowly defined interfaces provided by these \smr systems. For instance, 
to leverage ZooKeeper~\cite{zookeeper}, developers have to shoehorn their 
programs into the file IO interface defined by ZooKeeper.

>>>>

The second problem is that most existing \smr systems are not designed to 
support unmodified server programs. To utilize existing \smr services such as 
ZooKeeper~\cite{zookeeper}, developers often have to rewrite their code 
to orchestrate server programs into the narrowly defined interfaces 
provided by these \smr systems.
